### 2015-09-24 README.Rmd
plantminer is now defunct

You need API keys for Encyclopedia of Life (EOL), Tropicos, and Plantminer.

@@

	<td style="text-align:left;">Plantminer</td>
	<td style="text-align:left;"><code>plantminer</code></td>
	<td style="text-align:left;"><a href="http://www.plantminer.com/help">link</a></td>
	<td style="text-align:left;"><a href="http://www.plantminer.com/help">link</a></td>

>>>>

You need API keys for Encyclopedia of Life (EOL), and Tropicos.

@@
